---
title: "Google Maps Data Check"
output: html_document
date: "Last compiled on `r format(Sys.time(), '%B %d %Y')`"
knit: (function(inputFile, encoding) {
  root_dir <- rprojroot::find_rstudio_root_file();
  rmarkdown::render(inputFile, encoding = encoding, output_dir = paste0(root_dir, "/output"), knit_root_dir = root_dir) })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

source('code/functions.r')
```

### Load data
```{r load data}
gmaps_list <- lapply(states, function(x) data.table::fread(
  paste0("data/distance_matrix_gmaps/", x, "_weighted_gmaps_dist_mat.csv"),
  colClasses = c(rep("character", 2), "numeric", "character", rep("numeric", 2),
                 rep("character", 2), rep("numeric", 7))
))
names(gmaps_list) <- states
```

### Validity by travel mode
This table shows the number and proportion of valid and invalid responses for the hospital - ZIP code pairs, separated by state.
Proportions sum to 1 within state and travel mode.
```{r, results = 'asis'}
gmaps_list |>
  map(~ select(., distance_driving_m, distance_transit_m)) |>
  map(~ pivot_longer(.,
    cols = c(distance_driving_m, distance_transit_m),
    names_pattern = "distance_(.*)",
    names_to = "travel_mode",
    values_to = "distances"
  )) |> 
  bind_rows(.id = "state") |>
  mutate(
    validity = if_else(distances == -1, "Invalid", "Valid"),
    travel_mode = gsub("_m", "", travel_mode)
  ) |>
  count(state, travel_mode, validity) |>
  group_by(state, travel_mode) |>
  mutate(proportion = prop.table(n)) |>
  knitr::kable(digits=4)
```

### Number of ZIP codes that have no valid google response
This table shows the number and proportion of hospital - ZIP code pairs that have a valid drive or transit distance.
Proportions sum to 1 within state.
```{r, results = 'asis'}
gmaps_list |>
  bind_rows(.id = "state") |>
  mutate(validity = if_else(if_all(.cols = c(distance_driving_m, distance_transit_m), ~ . == -1), "No Valid Distance", "Has Valid Distance")) |>
  count(state, validity) |>
  group_by(state) |>
  mutate(proportion = prop.table(n)) |>
  knitr::kable(digits=4)
```

